manuscript_outline

### 2025-07-18 docs/manuscript/paper.Rmd
rerender with fixed docx template

---
title: ""
output:  
  bookdown::word_document2:
    toc: false
    number_sections: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: ecological-applications.csl
bibliography: references.bib
---

>>>>

---
title: ""
output:  
  bookdown::word_document2:
    toc: false
    number_sections: false
    reference_docx: presubmission-template.docx
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: ecological-applications.csl
bibliography: references.bib
---
